Finding Subgraphs With Side Constraints\thanks{This research was supported by the Engineering and Physical Sciences Research Council [grant number EP/P026842/1]}

### 2021-01-14 paper/paper.tex
Adding Jess sentences and cites

\subsection{Temporal Subgraph Problems}\label{section:temporalgraphs}

In a \emph{temporal graph}, edges are labelled with some kind of timestamp---here we will use
integers. Temporal pattern matching and counting has applications in ??. There are at least three
common kinds of temporal subgraph isomorphism. In an \emph{exact} subisomorphism, times are simply
labels that must match exactly. If we look at \cref{figure:littlegraphs}, now ignoring vertex labels
but using the edge labels to carry the timestamps,
\begin{lstlisting}
letting l be 1
letting e be 3

>>>>

\subsection{Temporal Subgraph Problems}\label{section:temporalgraphs}
In a \emph{temporal graph}, edges are labelled with timestamps that denote times when edges are active---here we use
integers as timestamps.  Including information on the timing of edges substantially increases the modelling power of these graphs, allowing them to 
more accurately reflect the structure and dynamics of a wide variety of real-world systems (e.g. trade networks, changing contact networks, transport networks), 
and address optimisation questions in which the timing of edges is fundamental.

As algorithms and formalisms have become available for temporal graphs, examples of their application have become widespread \cite{holmeReview}, 
notably including applications within epidemiology \cite{temporalEpi} and computational social science \cite{socialTemporalCite}.
Because the use of temporal graphs has spread beyond theoretical researchers, the ability to rapidly define and experiment with 
new problem definitions and constraints is valuable - practitioners are unlikely to define bespoke algorithms for novel problems as they arise.

%Temporal graphs 
% why being able to try new constraints easily is useful for practitioners

%In a \emph{temporal graph}, edges are labelled with some kind of timestamp---here we will use
%integers. Temporal pattern matching and counting has applications in ??. 
There are at least three
common kinds of temporal subgraph isomorphism. In an \emph{exact} subisomorphism, times are simply
labels that must match exactly. If we look at \cref{figure:littlegraphs}, now ignoring vertex labels
but using the edge labels to carry the timestamps,
\begin{lstlisting}
letting l be 1
letting e be 3
